\begin{abstract}
二维条码(2D Barcode)是用某种特定的几何图形按一定规律在平面（二维方向上）
分布的黑白相间的图形记录数据信息的符号。不同于一维条码，其可以在纵向和横向两
个方位同时表达信息，因此具有很大的信息密度。二维条码可以分为矩阵式和堆叠式二
维条码。目前世界上主流的二维条码，有QR码（快速响应矩阵码）、Data Matrix码、
PDF417码等。其中Data Matrix码由于可以在很小的空间内记录较多的信息，因此在工业流水线上有较多的应用。

Data Matrix码由于其编码特点，识别较慢。现有的基于Hough直线检测的定位算法速度较慢，不能满足工业上实时性要求。本文提出了一个快速定位算法，并且基于OpenCV完成了设计和测试。经过实验，证明本算法可以满足工业实时性要求。

同时，本文对二维码识别技术中涉及到的编码、图像处理以及开发用OpenCV都做了研究。

\keywords{Data Matrix \quad 二维码 \quad 定位算法 \quad 图像处理}
\end{abstract}


\begin{englishabstract}
The two-dimension barcode (2D barcode) is a symbol which record data
information using black and white graphics modules with a certain regular in
two-dimension directions (horizontal and vertical). Unlike one-dimension barcode,
2D barcode can express information in two directions, which determines its higher
data density. The 2D barcode can be categorized into two classes, matrix mode and
stack mode. And the most popular 2D barcode present are QR code, Data Matrix code,
PDF417 code, etc. Data Matrix Codes can store many information in small area, so it'f very popular in industry.

Because of it's special decode rule, the reading speed of Data Matrix is slow. Those algorithms that based on Hough Transform cannot meet industries' time need. We develop a fast localizing algorithm and deployed on OpenCV. The experiment result shows that this algorithm can meet the real-time need.

Meanwhile, we also researched the topics of decoding rule, image processing and OpenCV that related to 2-D barcode reading.

\englishkeywords{Data Matrix \quad 2-D barcode}
\end{englishabstract}
